---
title: "Hectorville Cricket Club Player Reviews"
subtitle: "Season `r substring(params$selected_season,4,5)`/`r substring(params$selected_season,7,8)`"
author: "Simon Thwaites"
date: "`r format(Sys.time(), '%d %B, %Y')`" # use system time and make human readable,e.g., 04 July, 2022
# output: pdf_document
output: html_document
params:
  review_years: NA
  selected_season: NA
  nResponses: NA
  season_data: NA
  allYears: NA
  groupByGrade: FALSE
  levels_react: NA
  wc.max.words: NA
  wc.min.freq: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE)

library(kableExtra)

options(dplyr.summarise.inform = FALSE)

## create plotting function for summary plots
summaryPlots <- function(allYears_df, allYears_df_selection, allYears_df_newName, summaryPlotYearsSelection, summaryGroupByGrade) {
  # summaryPlotYearsSelection is a reacctive from outside the module so must be passed directly as they cannpt access reactives outside of the module namespace
  
  
  
  plotData <- select(allYears_df, allYears_df_selection, `Grade most played`, Season) %>%
    filter(Season %in% summaryPlotYearsSelection)
  # filter(Season %in% summaryPlotYearsSelection())
  
  colnames(plotData) <- c(allYears_df_newName, "Grade", "Season") # assign new col names
  
  plotData <- plotData %>%
    mutate(Season = factor(Season), # make Season and Grade factors for plotting
           Grade = factor(Grade))
  
  if (summaryGroupByGrade == TRUE) {
    
    df_mean <- plotData %>%
      group_by(Grade, Season) %>%
      summarize(average = round(mean(.data[[allYears_df_newName]]), 2) ) %>%
      ungroup()
    
    p <- plotData %>%
      ggplot(aes(x = Season, y = .data[[allYears_df_newName]], fill = Grade)) +
      geom_boxplot(alpha = 0.5) +
      
      geom_point(data = df_mean,
                 mapping = aes(x = Season, y = average),
                 color="red",
                 position = position_dodge2(width = 0.7,
                                            preserve = "single"),
                 show.legend = FALSE,
                 na.rm=TRUE) +
      geom_line(data = df_mean,
                mapping = aes(x = Season, y = average, group=Grade, color = Grade),
                position = position_dodge2(width = 0.7,
                                           preserve = "single"),
                show.legend = FALSE,
                na.rm=TRUE)
    
    # p
    
    # html output only
    ggplotly(p) %>%
      layout(boxmode = "group")
    
  } else {
    df_mean <- plotData %>%
      group_by(Season) %>%
      summarize(average = round(mean(.data[[allYears_df_newName]]), 2) ) %>%
      ungroup()
    
    p <- plotData %>%
      ggplot(aes(x = Season, y = .data[[allYears_df_newName]])) +
      geom_boxplot(alpha = 0.5) +
      
      geom_point(data = df_mean,
                 mapping = aes(x = Season, y = average),
                 color="red",
                 show.legend = FALSE) +
      geom_line(data = df_mean,
                mapping = aes(x = Season, y = average, group = 1), # want to connect all the data points and we can specify that using group=1
                color = "red",
                show.legend = FALSE)
    
    
    p <- ggplotly(p) # plotly for html output only
    
    p
  }
}

newNames <- c("teamPerformance",                                       
              "yourPerformance",                                                                    
              "training",                                                                             
              "presentationNights",                                                      
              "selectionNights",                                                         
              "clubFunctions",                                                                        
              "gamedayPrep")

# reactive dataframe with only the quantitative metrics
df_quant_seasonData <- params$season_data[, 3:9] %>% 
  `colnames<-` (newNames) %>%        # special piping with setting colnames
  tibble::rowid_to_column("ID") %>%  # add id column
  pivot_longer(!ID, names_to = "ScoreName", values_to = "ScoreValue")  # make long

plotData <- params$season_data
yesCount <- plotData %>% 
  filter(`Do you plan on playing next season?` == "Yes") %>% 
  nrow()
```

## Executive Summary

This report details the HCC Player Reviews for Season `r substring(params$selected_season,4,5)`/`r substring(params$selected_season,7,8)`. There were `r params$nResponses` overall respondents, with `r yesCount` indicating they will play next year. This report contains: a summary of the current season, the seasonal trends, and all anonymised text responses for the current season. Overall, there appears to be a general upward trend in all metrics except for ratings of individual performance.  

This report is not optimised for mobile viewing, but you'll deal with it. If you accidentally change any plot windows when navigating/zooming on the page, you can reset the plot window by hitting the "autoscale" button towards the top right of each plot (looks like an X but with arrow heads).

Click on certain plot elements to interrogate the data further, or turn on/off groupings through the plot legends if you want to isolate certain groupings (note this will likely shag some of the grouping alignments as I haven't yet allowed for this to be dealt with nicely).

[Github repo for those programmatically inclined.](https://github.com/simon-thwaites/HCC-Reviews_distribution)

### Current Season

#### Grade most played?

```{r grade, out.width='80%'}
## grade most played
p <- plotData %>% 
  plot_ly(labels = ~`Grade most played`, type = 'pie', domain = list(row = 0, column = 0))
p
```

#### Playing next season?

```{r playing, out.width='80%'}
p <- plotData %>% 
  plot_ly(labels = ~`Do you plan on playing next season?`, type = 'pie', domain = list(row = 0, column = 1)) 
p
```

#### Season Summary

```{r violin}
plotData <- df_quant_seasonData #%>%
# filter(ScoreName %in% input$varSelection)
# make order of Name an ordered factor to stop ggplot reordering the xData
plotData$ScoreName <- ordered(plotData$ScoreName, levels = params$levels_react)

# change the display names of the metrics
plotData <- plotData %>% 
  mutate(ScoreName = recode(ScoreName, 
                            "teamPerformance" = "Team Performance",                                       
                            "yourPerformance" = "Your Performance",
                            "training" = "Training",
                            "presentationNights" = "Presentation Nights",
                            "selectionNights" = "Selection Nights",
                            "clubFunctions" = "Club Functions",
                            "gamedayPrep" = "Gameday Preparation"))

p <- plotData %>%
  plot_ly(
    x = ~ScoreName,
    y = ~ScoreValue,
    split = ~ScoreName,
    type = 'violin',
    box = list(visible = T),
    opacity = 0.75,
    points = 'all',
    jitter = 0.2,
    meanline = list(visible = T)
  ) %>%
  layout(
    xaxis = list(
      title = "Metric"
    ),
    yaxis = list(
      title = "Score",
      zeroline = T,
      range = c(-1,11)
    )
  ) %>%
  hide_legend()
p
```

### Seasonal trends

#### **Team Performance**

```{r trend1}
summaryPlots(params$allYears, "Team performance (from your grade most played):", "TeamPerformance", params$review_years, params$groupByGrade)
```

#### **Your Performance**

```{r trend2}
summaryPlots(params$allYears, "Your performance:", "yourPerformance", params$review_years, params$groupByGrade)
```

#### **Training**

```{r trend3}
summaryPlots(params$allYears, "Training:", "training", params$review_years, params$groupByGrade)
```

#### **Presentation Nights (Saturdays)**

```{r trend4}
summaryPlots(params$allYears, "Presentation nights (Saturdays):", "presentationNights", params$review_years, params$groupByGrade)
```

#### **Selection Nights (Thursdays)**

```{r trend5}
summaryPlots(params$allYears, "Selection nights (Thursdays):", "selectionNights", params$review_years, params$groupByGrade)
```

#### **Club Functions**

```{r trend6}
summaryPlots(params$allYears, "Club Functions", "clubFunctions", params$review_years, params$groupByGrade)
```

#### **Game Day Preparation**

```{r trend7}
summaryPlots(params$allYears, "Game day preparation", "gamedayPrep", params$review_years, params$groupByGrade)
```

### Text Responses

#### **What were the standout positives from the season?**

```{r text1, out.width="70%"}
text.colnames <- c("text.positives",
                   "text.negatives",
                   "text.training",
                   "text.presentations",
                   "text.selections",
                   "text.gamedayprep",
                   "text.funcideas",
                   "text.comments",
                   "text.moment")

text.data <- params$season_data %>% 
  rename(text.positives = `What were the standout positives from the season?`,
         text.negatives = `What were the standout negatives from the season?`,
         text.training = `How could we improve training?`,
         text.presentations = `How could we improve presentation nights?`,
         text.selections = `How could we improve selection nights?`,
         text.gamedayprep = `How could we improve game day preparation?`,
         text.funcideas = `Do you have any ideas for Club functions?`,
         text.comments = `Any other comments?`,
         text.moment = `What was your moment of the season?`) %>% 
  select(all_of(text.colnames)) %>% 
  # Note: Using an external vector in selections is ambiguous.
  # Use `all_of(text.colnames)` instead of `text.colnames` to silence this message.
  # See <https://tidyselect.r-lib.org/reference/faq-external-vector.html>.
  replace_contraction() %>% 
  { gsub("[’]", "", .) }
# With pipe your data are passed as a first argument to the next function, 
# so if you want to use it somewhere else you need to wrap the next line in {} and use . as a data "marker".

wordcloud_rep <- repeatable(wordcloud)

word.cloud.scale <- c(3,0.5)

words <- createTDM(text.data, 1)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table1}
t.data <- data.frame(params$season_data$`What were the standout positives from the season?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```

#### **What were the standout negatives from the season?**

```{r text2, out.width="70%"}
words <- createTDM(text.data, 2)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table2}
t.data <- data.frame(params$season_data$`What were the standout negatives from the season?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```

#### **How could we improve training?**

```{r text3, out.width="70%"}
words <- createTDM(text.data, 3)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table3}
t.data <- data.frame(params$season_data$`How could we improve training?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```

#### **How could we improve presentation nights?**

```{r text4, out.width="70%"}
words <- createTDM(text.data, 4)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table4}
t.data <- data.frame(params$season_data$`How could we improve presentation nights?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```

#### **How could we improve selection nights?**

```{r text5, out.width="70%"}
words <- createTDM(text.data, 5)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table5}
t.data <- data.frame(params$season_data$`How could we improve selection nights?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```

#### **How could we improve game day preparation?**

```{r text6, out.width="70%"}
words <- createTDM(text.data, 6)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table6}
t.data <- data.frame(params$season_data$`How could we improve game day preparation?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```

#### **Do you have any ideas for Club functions?**

```{r text7, out.width="70%"}
words <- createTDM(text.data, 7)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table7}
t.data <- data.frame(params$season_data$`Do you have any ideas for Club functions?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```

#### **Any other comments?**

```{r text8, out.width="70%"}
words <- createTDM(text.data, 8)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table8}
t.data <- data.frame(params$season_data$`Any other comments?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```

#### **What was your moment of the season?**

```{r text9, out.width="70%"}
words <- createTDM(text.data, 9)
wordcloud_rep(names(words), words,  
              scale = word.cloud.scale,
              min.freq = params$wc.min.freq, max.words= params$wc.max.words,
              colors = brewer.pal(8, "Dark2"))
```

```{r table9}
t.data <- data.frame(params$season_data$`What was your moment of the season?`)
colnames(t.data) <- "Responses"
kable(t.data) %>% kable_styling()
```
